---
output:
  word_document: default
  html_document: default
---
## Exploring Age at First Marriage
### Julia Perez

Data from https://www.kaggle.com/datasets/thedevastator/median-age-at-first-marriage-in-america

```{r Libraries, include = FALSE}
library(tidymodels)
library(tidyverse)
library(skimr)
library(ggcorrplot)
library(GGally)
library(gridExtra)
library(caret)
library(vip)
library(VIM)
library(mice)
library(ranger)
library(glmnet)
library(MASS)
library(car)
library(lmtest)
library(splines)
library(e1071)
library(ROCR)
library(randomForest)
library(xgboost)
library(usemodels)
library(readxl)
```

### Import Data
```{r Import}
marriage <- read_csv("Median Age at First Marriage .csv")
head(marriage)

marriage <- marriage %>% 
  rename(Age = 'Median Age', Pop.Density = 'Population Density per Sq Mi', State = Name) %>% 
  mutate(across(where(is_character),as_factor))
```

### Exploratory Data Analysis
```{r EDA}
ggplot(marriage, aes(Age)) +
  geom_boxplot()

ggplot(marriage, aes(State, Age, color = TimeFrame)) +
  geom_point() +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(x = "State")
# See a trend of median marriage age increasing over time

ggplot(marriage, aes(Pop.Density, Age)) +
  geom_point() +
  scale_x_log10() +
  geom_smooth(method = lm)
# As the log of population density increases, so does the median age of marriage
```


### Train & Test Split
```{r Split}
set.seed(123)

marriage_split <- initial_split(marriage, prop = 0.80, Age)
train <- training(marriage_split)
test <- testing(marriage_split)
```

### Linear Model
```{r LM}
age_recipelm <- recipe(Age ~ State + TimeFrame + Pop.Density, train) %>%
  step_log(Pop.Density) %>% 
  step_dummy(all_nominal(), -all_outcomes())

age_model <- 
  linear_reg() %>% 
  set_engine("lm")

age_wkflw1 <- workflow() %>% 
  add_model(age_model) %>% 
  add_recipe(age_recipelm)

lm_fit_all <- fit(age_wkflw1, train)
summary(lm_fit_all$fit$fit$fit)
```

This model shows that only Louisiana, Wisconsin, and TimeFrame are statistically significant. Adjusted R-squared 0.96.

```{r Refine LM}
# Likely correlation between State and Pop.Density, trying models with just State and Time Frame
age_recipe_state <- recipe(Age ~ State + TimeFrame, train) %>%
  step_dummy(all_nominal(), -all_outcomes())

age_model <- 
  linear_reg() %>% 
  set_engine("lm")

age_wkflw_state <- workflow() %>% 
  add_model(age_model) %>% 
  add_recipe(age_recipe_state)

lm_fit_state <- fit(age_wkflw_state, train)
summary(lm_fit_state$fit$fit$fit)

# In this model, more states have a statistically significant impact on median marriage age. Adjusted R-squared shows only a very slight improvement.

# Model just using Pop.Density and TimeFrame
age_recipe_pop <- recipe(Age ~ TimeFrame + Pop.Density, train) %>%
  step_log(Pop.Density) %>% 
  step_dummy(all_nominal(), -all_outcomes())

age_model <- 
  linear_reg() %>% 
  set_engine("lm")

age_wkflw_pop <- workflow() %>% 
  add_model(age_model) %>% 
  add_recipe(age_recipe_pop)

lm_fit_pop <- fit(age_wkflw_pop, train)
summary(lm_fit_pop$fit$fit$fit)

# Although Pop.Density and TimeFrame are both significant variables, the adjusted R-squared shows a large decrease to 0.691.
```

We will use the model with State and TimeFrame.

### Performance on Test Set
```{r Test}
lm_fit_state %>%
  predict(test) %>% 
  bind_cols(test) %>% 
  metrics(truth = Age, estimate = .pred)
```

The R-squared on this model is 0.72 which does suggest that this model is not overfitting.



